### 2019-06-05 2-Chapters/1-Chapter/chapter1.tex
Je viens de faire un premier jet (brouillon)
- de l'abstract FR/EN
- du résumé en français
Starting to try to add meta data

% ----------------------------------------------------------------------------
\section{List of publications}
\label{sec:1:listPublications}

@@

\paragraph{Seminars}
    I gave some presentations in the following events:
    SequeL team seminar at Inria Lille in September and December $2017$, and June $2019$;
    SCEE team seminar at CentraleSupélec, Rennes campus, in October $2017$, February $2018$ and June $2019$;
    as well as
    for the GDR ISIS day held in Issy-les-Moulineaux on November $2017$,
    for the brown-bag seminar at ENSAI in Bruz in January $2018$,
    for the weekly seminar at CMAP lab at École Polytechnique in October $2018$,
    for the weekly seminar of the PANAMA project-team at IRISA / Inria Rennes in May $2019$.

\paragraph{Tutorial}
    I gave a tutorial on the Julia language, at IETR seminar in Vannes in June $2018$,
    with Pierre Haessig (\texttt{pierreh.eu}), see \href{https://HAL.Inria.fr/cel-01830248}{\texttt{HAL.Inria.fr/cel-01830248}}.

\paragraph{Training}
    I was also in charge of ``GouTP'' training sessions for about $30$ PhD students at CentraleSupélec Rennes.
    We had a lot of various $1$h training sessions between January $2017$ and June $2019$,
    and I gave about $12$ training sessions, on various topics including Python, \texttt{git}, HAL and arXiv, the Julia language and Bib\TeX{}.

@@

\paragraph{Conferences}
    I attended the following conferences:
	\emph{International Conference on Communication} ICC (Paris), May $2017$,
    \emph{Conference on Learning Theory} COLT (Amsterdam), July $2017$,
    \emph{Conference on Cognitive Radio Oriented Wireless Networks} CROWNCOM (Lisboa), September $2017$,
    \emph{Conference on Algorithmic Learning Theory} ALT (Lanzarote), April $2018$,
    \emph{Wireless Communication and Networking Conference} WCNC (Barcelona), April $2018$,
	\emph{International Conference on Telecommunication} ICT (Saint-Malo), June $2018$,
    \emph{Wireless Communication and Networking Conference} WCNC (Marrakech), April $2019$,
    \emph{Colloque francophone de traitement du signal et des images} GRETSI (Lille), August $2019$.

\paragraph{Seminars}
    I attended the following seminars:
	\emph{Workshop Learn with Earning} (Rotterdam), May $2018$,
	\emph{Workshop on Optimization and Learning} (Toulouse), September $2018$,
	\emph{European Workshop on Reinforcement Learning} (Lille), October $2018$,

\paragraph{Responsabilities}
    I was the president of the PhD Students Association of IETR lab (ADDI, \texttt{addi.asso.insa-rennes.fr}) in $2017$.
    I was notably in charge of organizing the PhD Students day at Rennes, in June $2017$, with about $350$ people, and presentation of a research poster\footnote{~See \href{https://HAL.Inria.fr/hal-02013839}{\texttt{HAL.Inria.fr/hal-02013839}}}
    I also helped for the organization and presented another poster\footnote{~See \href{https://HAL.Inria.fr/hal-02013847}{\texttt{HAL.Inria.fr/hal-02013847}}} at the ``IETR : Interagir Évaluer Transmettre Réunir'' seminar, held in Vannes in June $2018$.

\paragraph{Reviews}
	for \emph{European Workshop on Reinforcement Learning}\footnote{~EWRL 2018, see \href{https://ewrl.wordpress.com/ewrl14-2018}{\texttt{ewrl.wordpress.com/ewrl14-2018}}} (Lille), in October $2018$, I reviewed $5$ papers.
	I helped colleagues for articles submitted at international conferences \emph{AISTATS} $2019$, \emph{NeurIPS} $2017$ et $2018$, and \emph{COLT} $2018$ and $2019$, for about 10 \emph{reviews}.

\paragraph{System Administrator}
	maintaining our workstations running GNU/Linux and Windows
	at SCEE team,
	and our cognitive radio test-bed using USRP cards and the GNU Radio software,
	from January $2017$ to September $2018$.

>>>>

% ----------------------------------------------------------------------------
\section{List of publications and other experiences}
\label{sec:1:listPublications}

@@

\paragraph{Seminars.}
    I gave some presentations in the following events:
    SequeL team seminar at Inria Lille in September and December $2017$, and June $2019$;
    SCEE team seminar at CentraleSupélec, Rennes campus, in October $2017$, February $2018$ and June $2019$;
    as well as
    for the GDR ISIS day held in Issy-les-Moulineaux on November $2017$,
    for the brown-bag seminar at ENSAI in Bruz in January $2018$,
    for the weekly seminar at CMAP lab at École Polytechnique in October $2018$,
    for the weekly seminar of the PANAMA project-team at IRISA / Inria Rennes in May $2019$.

\paragraph{Tutorial.}
    I gave a tutorial on the Julia language, at IETR seminar in Vannes in June $2018$,
    with Pierre Haessig (\texttt{pierreh.eu}), see \href{https://HAL.Inria.fr/cel-01830248}{\texttt{HAL.Inria.fr/cel-01830248}}.

\paragraph{Training.}
    I was also in charge of ``GouTP'' training sessions for about $30$ PhD students at CentraleSupélec Rennes.
    We had a lot of various $1$h training sessions between January $2017$ and June $2019$,
    and I gave about $12$ training sessions, on various topics including Python, \texttt{git}, HAL and arXiv, the Julia language and Bib\TeX{}.

@@

\paragraph{Conferences.}
    I attended the following conferences:
	\emph{International Conference on Communication} ICC (Paris), May $2017$,
    \emph{Conference on Learning Theory} COLT (Amsterdam), July $2017$,
    \emph{Conference on Cognitive Radio Oriented Wireless Networks} CROWNCOM (Lisboa), September $2017$,
    \emph{Conference on Algorithmic Learning Theory} ALT (Lanzarote), April $2018$,
    \emph{Wireless Communication and Networking Conference} WCNC (Barcelona), April $2018$,
	\emph{International Conference on Telecommunication} ICT (Saint-Malo), June $2018$,
    \emph{Wireless Communication and Networking Conference} WCNC (Marrakech), April $2019$,
    \emph{Colloque francophone de traitement du signal et des images} GRETSI (Lille), August $2019$.

\paragraph{Seminars.}
    I attended the following seminars:
	\emph{Workshop Learn with Earning} (Rotterdam), May $2018$,
	\emph{Workshop on Optimization and Learning} (Toulouse), September $2018$,
	\emph{European Workshop on Reinforcement Learning} (Lille), October $2018$,

\paragraph{Responsabilities.}
    I was the president of the PhD Students Association of IETR lab (ADDI, \texttt{addi.asso.insa-rennes.fr}) in $2017$.
    I was notably in charge of organizing the PhD Students day at Rennes, in June $2017$, with about $350$ people, and presentation of a research poster\footnote{~See \href{https://HAL.Inria.fr/hal-02013839}{\texttt{HAL.Inria.fr/hal-02013839}}}
    I also helped for the organization and presented another poster\footnote{~See \href{https://HAL.Inria.fr/hal-02013847}{\texttt{HAL.Inria.fr/hal-02013847}}} at the ``IETR : Interagir Évaluer Transmettre Réunir'' seminar, held in Vannes in June $2018$.

\paragraph{Reviews.}
	for \emph{European Workshop on Reinforcement Learning}\footnote{~EWRL 2018, see \href{https://ewrl.wordpress.com/ewrl14-2018}{\texttt{ewrl.wordpress.com/ewrl14-2018}}} (Lille), in October $2018$, I reviewed $5$ papers.
	I helped colleagues for articles submitted at international conferences \emph{AISTATS} $2019$, \emph{NeurIPS} $2017$ et $2018$, and \emph{COLT} $2018$ and $2019$, for about 10 \emph{reviews}.

\paragraph{System Administrator.}
	maintaining our workstations running GNU/Linux and Windows
	at SCEE team,
	and our cognitive radio test-bed using USRP cards and the GNU Radio software,
	from January $2017$ to September $2018$.

% WARNING
\vfill{}

\paragraph{Copyright notice.}
%
This document and the additional resources required to compile it (including \LaTeX{} code, Python snippets, images etc)
are \href{https://github.com/Naereen/phd-thesis/}{publicly published},
online at \href{https://github.com/Naereen/phd-thesis/}{\texttt{GitHub.com/Naereen/phd-thesis/}},
under the terms of the open-source \href{https://lbesson.mit-license.org/}{\emph{MIT License}}.

\TODOL{Open source the repository as soon as I defended my thesis!}

\begin{center}
    \textbf{Copyright 2016-2019, \copyright ~Lilian~Besson.}
\end{center}
